Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-03-02 journal paper/content/sec-intro.tex

%The main high-level question we ask is:
%that we focus on in this paper is:
%\begin{align}\label{eq:main-Q}
\asedit{We ask:}
\textbf{Whether and how does competition incentivize the adoption of better exploration algorithms?}
%\end{align}
This translates into a number of more concrete questions. While it is commonly assumed that better technology always helps, is this so under competition? Does increased competition lead to higher consumer welfare? How significant are the data feedback loops
%--- when more data leads to more users, which leads to even more data, etc. ---
and how they relate to the anti-trust considerations?
%Finding formalizations that admit meaningful answers is a major part of the overall challenge.
We offer a mix of theoretical results and numerical simulations, in which we study complex interactions between platforms' learning dynamics and users' self-interested behavior.

>>>>

\asedit{The main high-level question we ask is:}
%that we focus on in this paper is:
%\begin{align}\label{eq:main-Q}
%\asedit{We ask:}
\textbf{Whether and how does competition \asedit{between platforms} incentivize the adoption of better exploration algorithms?}
%\end{align}
This translates into a number of more concrete questions. While it is commonly assumed that better technology always helps, is this so under competition? Does increased competition lead to higher consumer welfare? How significant are the data feedback loops
%--- when more data leads to more users, which leads to even more data, etc. ---
and how they relate to the anti-trust considerations?
%Finding formalizations that admit meaningful answers is a major part of the overall challenge.
We offer a mix of theoretical results and numerical simulations, in which we study complex interactions between platforms' learning dynamics and users' self-interested behavior. \asedit{Prior work on exploration vs. competition targets technically very different models of competition which are not amenable to our high-level question (as we discuss in Section~\ref{sec:related-work}).}
